Data Preparation

### 2019-01-09 Data Preparation.Rmd
extracts final grades

d_reduce <- d_reduce[!duplicated(d_reduce),]
```
###Extracting grades

>>>>

d_reduce <- d_reduce[!duplicated(d_reduce),]
```
###Extracting grades
We notice that there are several values under `Grade` for the same course. We are interested in keeping only the final grades, corresponding to the rows where `Appraisal Title` is marked as "Grade supervisor". 
So lets extract the grades and add the course concentration by keeping the first three letters of the `Code`:

```{r}
d_grade <- d_reduce %>%
  filter(`Appraisal Title` == "Grade supervisor") %>%
  mutate(`Course concentration` = substr(Code, start = 1, stop = 3))

d_grade <- d_grade[!duplicated(d_grade),]
```
